---
params:
  title: "Snack map"
  author: "Matt Malishev"
  social: "@darwinanddavis" 
  primary: "#9d9d9d"
  secondary: "#FFFFFF"
output: 
  html_document:
    theme: "cosmo"
    css: css/style.css
    includes:
      before_body: header.html
      after_body: footer.html
---


<link rel="stylesheet"href="//fonts.googleapis.com/css?family=Quicksand:300,400,600,700&amp;lang=en"/>


<!-- css for tabs -->
<style type="text/css">

.nav>li>a{
    position: relative;
    display: block;
    padding: 10px 15px;
}

.nav-pills>li>a:hover{
  background: `r params$secondary`;
  color: `r params$secondary`;
  opacity:0.6;
}

.nav-pills>li>a:focus, .nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus {
  background: `r params$primary`;
  background-color: `r params$secondary`;
}

</style>


```{r, set-options, echo = F, cache = T,results='hide',message=F,warning=F}
options(width=25,tinytex.verbose = TRUE, width.cutoff=25)
knitr::opts_chunk$set(
 eval = T, # run all code
 echo = F, # show code chunks in output 
 tidy=T, # make output as tidy
 message = F,  # mask all messages
 warning = F, # mask all warnings 
 size="small", # set code chunk size,
 tidy.opts=list(width.cutoff=25) # set width of code chunks in output
)

# tinytex::install_tinytex()
# require(tinytex)
# install.packages("pacman")
# require(pacman)


```

```{r,load_data,eval=T,echo=F,results='hide', message=F,warning=F}
suppressWarnings(pacman::p_load(dplyr,ggplot2,plotly,htmlwidgets,viridis,here,dplyr,readr,purrr,stringr,leaflet,leaflet.extras,scales,colorspace,htmltools))

# sets 'fh' from individual code chunks in tabs 
fh <- "_master" #"Favourites"
ff <- here::here("data")
# id_df <- paste0(ff,"/id_df.csv") %>% read_csv # get custom col and map styles


# get place data ----------------------------------------------------------
fn <- fh %>% str_replace_all(" ","_") %>% str_to_lower
m <- ff %>% paste0("/final_locations/", fn,".Rda") %>% readRDS
```



```{r,make_map,eval=F,echo=F,results='hide',message=F,warning=F}
# map ----------------------------------------------------------------------
custom_tile <- "http://b.sm.mapstack.stamen.com/((mapbox-water,$f2f7ff[hsl-color]),(positron,$f2f7ff[hsl-color]),(buildings,$f2f7ff[hsl-color]),(parks,$2c403b[hsl-color]))/{z}/{x}/{y}.png"

# pars
df <- m %>% .[[fh]]
ttl <- df$fh %>% str_to_title() %>% unique
setview <- c(144.960576, -37.81685)
opac <- 0.7
zoom = 13

# pulse icons
marker_pulse <- makePulseIcon(
  color = m$colv,
  iconSize = 20,
  animate = T,
  heartbeat = 5
)

# iconset 
iconSet = pulseIconList(makePulseIcon(color = m$colv))
  

# easy buttons 
locate_me <- easyButton( # locate user
  icon="fa-crosshairs", title="Zoom to my position",
  onClick=JS("function(btn, map){ map.locate({setView: true}); }"));

reset_zoom <- easyButton( # reset zoom 
  icon="fa-globe", title="Reset zoom",
  onClick=JS("function(btn, map){ map.setZoom(13);}"));  

# text labels 
style <- list(
  "color" = m$colv,
  "font-weight" = "normal",
  "padding" = "8px"
)

# label options
text_label_opt <- labelOptions(noHide = F, direction = "top", textsize = "15px",
                               textOnly = F, opacity = 0.7, offset = c(0,0),
                               style = style, permanent = T
)

# layer options 
layer_options <- layersControlOptions(collapsed = F)


# title 
map_title <- tags$style( 
  HTML(".leaflet-control.map-title { 
       transform: translate(-50%,20%);
       position: fixed !important;
       left: 50%;
       text-align: center;
       padding-left: 10px; 
       padding-right: 10px; 
       background: white; opacity: 0.5;
       font-size: 40px;
       }"
  ))

title <- tags$div(
  map_title, HTML(ttl)
)  


# map
map <- leaflet() %>%  # initiate the leaflet map object
  setView(setview[1], setview[2], zoom = zoom) %>%
  addTiles(
    # df$style %>% unique
    custom_tile,
    group = c(fh),
    ) %>%  # add map tiles to the leaflet object
  # addPulseMarkers(df$lon, df$lat,
  #                 icon = iconSet,  # marker_pulse,
  #                 popup = df$popup,
  #                 label = df$label,
  #                 popupOptions = text_label_opt,
  #                 labelOptions= text_label_opt,
  #                 group = fh
  # ) %>%
addCircleMarkers(df$lon, df$lat,
                 radius = 10,
                 stroke = T,
                 weight = 3,
                 opacity = opac,
                 color = df$colv,
                 fillColor = df$colv,
                 popup = df$popup,
                 label = df$label,
                 popupOptions = text_label_opt,
                 labelOptions= text_label_opt,
                 group = fh %>% str_to_title()
) %>%
  addLayersControl(
    baseGroups = c(fh %>% str_to_title()
                   # ,layer2,layer3
                   ),
    options = layer_options) %>%
  # hideGroup(c(layer2,layer3)) %>% 
  addControl(title, "bottomleft", className = "map-title") %>% 
  # addControl(control_box, "topright", className = "layers-base") %>% 
  addEasyButton(reset_zoom) %>% 
  addEasyButton(locate_me) 

map 

```


# <span style="font-size:200%;">`r params$title`</span> {.tabset .tabset-fade .tabset-pills}  

#### `r params$author` | `r params$social`   

### Select your snack and explore the map      

Switch among the tabs for different categories. Use the 'Locate me' and 'Reset zoom' buttons in the map to recentre. More snack categories to come.        
  
## <span style="color:`r params$primary`;">Favourites</span>
```{r,echo=F,warning=F,message=F, width="100%",height="100%"}
# test mapdeck speed after uploading to git
fh <- "favourites"
<<make_map>> 
```

## <span style="color:`r params$primary`;">Coffee</span>
```{r,echo=F,warning=F,message=F,width="100%",height="100%"}
fh <- "coffee"  
<<make_map>> 
```

## <span style="color:`r params$primary`;">Happy hour</span>
```{r,echo=F,warning=F,message=F,width="100%",height="100%"}
fh <- "happy_hour"  
<<make_map>> 
```

## <span style="color:`r params$primary`;">Dumplings</span>
```{r,echo=F,warning=F,message=F,width="100%",height="100%"}
fh <- "dumplings"  
<<make_map>> 
```

## <span style="color:`r params$primary`;">Night moves</span>
```{r,echo=F,warning=F,message=F,width="100%",height="100%"}
fh <- "nightmoves"  
<<make_map>> 
```

## <span style="color:`r params$primary`;">Rooftop</span>
```{r,echo=F,warning=F,message=F,width="100%",height="100%"}
fh <- "rooftop"  
<<make_map>> 
```

<!-- *** -->

